---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# realclearpolitics

<!-- badges: start -->
<!-- badges: end -->

The goal of realclearpolitics is to make it easy to download poll data and moving averages from realclearpolitics.com

## Installation

You can install the development version with

``` r
devtools::install_github("alexpavlakis/realclearpolitics")
```

## Example

If we want to scrape the RCP table of national polls from the 2012 presidential election, we can enter the RCP URL of interest as the `url` arguement of `get_rcp_polls`.

```{r load_polls}
library(realclearpolitics)

# Scrape the table of polls
url <- "https://www.realclearpolitics.com/epolls/2012/president/us/general_election_romney_vs_obama-1171.html"
polls <- get_rcp_polls(url = url)
head(polls)

# "Tidy" it up
tidied_polls <- tidy(polls)
head(tidied_polls)
```

If we want the RCP moving average, we can identify a race by its "id", which can be be found in the URL (e.g., the id for 2012 Obama-Romeny national polls is 1171), and use that the scrape the raw data behind RCP's charts.

```{r load_ma}
ma <- get_rcp_ma(id = 1171)

head(ma)

plot(ma) +
  ggplot2::ylim(0.4, 0.55) +
  ggplot2::scale_color_manual(values = c('blue', 'red'))

```
